\begin{thebibliography}{100}
    \setlength{\itemindent}{-1cm}
    \setlength\itemsep{0pt}
    \setlength{\parskip}{0pt}

    \bibitem{RC} Randell, C., Muller, H., \f{Context awareness by analysing accelerometer
        data}. The Fourth International Symposium on Wearable Computers IEEE Computer
        Society (pp. 175-176). 2000.
    \bibitem{GC} Cugola, G., Murphy, L., A., Picco, G., P., \f{Content-based 
        dispatching in a mobile environment}. Workshop su
        sistemi Distibuiti., 2000.
    \bibitem{AL2} Leonhardi, A., Rothermel, K., \f{A comparison of protocols for updating
        location information}. Cluster Computing, 2001.
    \bibitem{AL1} Leonhardi A., Nicu C., Rothermel K., \f{A map-based dead-reckoning
        protocol for updating location information}. Proceedings of 16th Int. Parallel and
        Distributed Processing Symposium, 2002.
    \bibitem{KR} Kjaergaard, M., B., Langdal, J., Godsk, T., Toftkjaer, T., \f{EnTracked:
        Energy-efficient robust position tracking for mobile devices}. 
    \bibitem{EG} Eugster, P., Felber, P., A., Guerraoui, R., \f{The many faces of
        publish/subscribe}. ACM Computing Survey., 2003.
    \bibitem{YH} Huang, Y., Garcia-Molina, H., \f{Publish/Subscribe in a Mobile 
        Environment}., MobiDe'01: ACM Int.
        Workshop on Data engineering for Wireless and Mobile access., 2004.
    \bibitem{AC} Civilis, A., Jensen, C. S., Pakalnis, S., \f{Techniques for efficient
        road network-network-based tracking of moving objects}. IEEE Trans. Data Eng., 2005.
    \bibitem{BE} Becker, C., Durr F., \f{On Location Models for Ubiquitous Computing}.
        Personal and Ubiquitous Computing., 2005.
    \bibitem{HI} Hinske, Steve., \f{Location Models}. Distributed Systems seminar., 2006.
    \bibitem{HU} Hunkeler, U., Truong, L., \f{MQTT-S - A publish/subscribe protocol
        for wireless sensor networks}. IEEE Conference on COMSWARE., 2008.
    \bibitem{WW} Frank, H., P., Charaf, H., \f{Mobile peer to peer (P2P) - A tutorial guide}.,
        John Wiley \& Sons, Ltd., 2009.
    \bibitem{HJ} Hong, J., Suh, E., Kim, S., J., \f{Context-aware systems: A literature
        review and classification}. POSMIS Lab, Industrial Management Engineering Building,
        Pohang University of Science Technology., 2009.
    \bibitem{AA} Ashfaque, A., Naznin, M., Islam, A., \f{Energy-efficient multiple
        targets tracking using target kinematics in wireless sensor networks}. IEEE
        Conference., 2010.
    \bibitem{ZS} Salvador, Z., Alzua, A., Larrea, M., Lafuente, A., 
        \f{A: Mobile XSiena: towards mobile publish/subscribe}., ACM
        International Conference on Distributed Event-Based Systems., 2010.
    \bibitem{AL} \f{Locations and Maps}. Dipetik April 21, 2013, dari Developer Android:
        http://www.developer.android.com/guide/topics/location/index.html
    \bibitem{VO} \f{Android Location API - Tutorial}. Dipetik April 21, 2013, dari Vogella:
        http://www.vogella.com/artivles/AndroidLocationAPI/article.html
    \bibitem{AQ} \f{ActiveMQ}. Dipetik April 21, 2013, dari ActiveMQ:
        http://www.activemq.com.
    %\bibliography{pustaka}

\end{thebibliography}
